Formalizing Stack Safety as a Security Property

### 2021-09-30 submission4/main.tex
Added exceptions to appendix

\begin{tabular}{l}
{\sc Call} \\
\judgmenttwobrlong[]
              {\(\codemap ~ (\mach ~ \PCname)\)}
%              {\(\components = \sealcon ~ \mach\)}
              {\(\components = \{\component | \sealcon ~ \mach[\component]\}\)}
              {\(\domMap' = \domMap[\components \mapsto \sealed{|\rts|}]\)}
                {\(\mach,(\domMap,\rts) \stepsto_C \domMap',(\retcon ~ \mach)::\rts\)} \\
\end{tabular}
\begin{tabular}{l}
{\sc ReturnFound} \\
\judgmenttwo[]
              {\(\mach \stepsto \mach' \in \target\)}
              {\(\components = \{\component | \domMap ~ \component = \sealed{|\rts|}\}\)}
              {\(\mach,(\domMap,\target::\rts) \stepsto_C \domMap[\components \mapsto \unsealed],\rts\)} \\
{\sc ReturnRec} \\
\end{tabular}
\begin{tabular}{l}
\judgmentbr[]
            {\(\mach,(\domMap,\rts) \stepsto_C \domMap',\rts'\)}
            {\(\components = \{\component | \domMap ~ \component = \sealed{|\rts|}\}\)}
            {\(\mach,(\domMap,\underscore::\rts) \stepsto_C \domMap'[\components \mapsto \unsealed],\rts'\)} \\
\end{tabular}
\begin{tabular}{l}
\end{tabular}

@@

From here, we see two natural ways to extend the work. First, we should thoroughly evaluate
other enforcement mechanisms, especially Cheri-based capability
systems. Second, we can further demonstrate
the functionality of our definitions by showing that they can be used to prove
the correctness of a programming logic with strengthened rules around calls and returns.

@@

%Text of appendix \ldots

>>>>

\begin{tabular}{l}
{\sc Call} \\
\judgmenttwobrlong[]
              {\(\codemap ~ (\mach ~ \PCname) = \callmap\)}
%             {\(\components = \sealcon ~ \mach\)}
              {\(\components = \{\component | \sealcon ~ \mach[\component]\}\)}
              {\(\domMap' = \domMap[\components \mapsto \sealed{|\rts|}]\)}
              {\(\mach,(\domMap,\rts) \stepsto_C \domMap',(\retcon ~ \mach)::\rts\)} \\
\end{tabular}
\begin{tabular}{l}
{\sc ReturnFound} \\
\judgmenttwo[]
            {\(\mach \stepsto \mach' \in \target\)}
            {\(\components = \{\component | \domMap ~ \component = \sealed{|\rts|}\}\)}
            {\(\mach,(\domMap,\target::\rts) \stepsto_C \domMap[\components \mapsto \unsealed],\rts\)} \\
{\sc ReturnRec} \\
\end{tabular}
\begin{tabular}{l}
\judgmentbr[]
            {\(\mach,(\domMap,\rts) \stepsto_C \domMap',\rts'\)}
            {\(\components = \{\component | \domMap ~ \component = \sealed{|\rts|}\}\)}
            {\(\mach,(\domMap,\underscore::\rts) \stepsto_C \domMap'[\components \mapsto \unsealed],\rts'\)} \\
\end{tabular}
\begin{tabular}{l}
\end{tabular}

@@

From here, we see two natural ways to extend the work. First, we should thoroughly evaluate
other enforcement mechanisms, especially Cheri-based capability
systems. Second, we can further demonstrate
the functionality of our definitions by using them to prove
the correctness of a programming logic with strengthened rules around calls and returns.

@@

Our core formalism already models control flow patterns in which a return skips over one or more callers to
reach a point further down the call stack. This is essentially the behavior of an exception; we need only add an
annotation representing the {\tt setjump} operation or equivalent to enable a ``return'' to an arbitrary point
not associated with a call. We add an annotation, {\sc SetJump}, and define a target label as either a call-return
or an exception, \(\mathit{TL} ::= \text{\sc CR} + \text{\sc EX}\), which annotates targets in the return stack.
\[\context \in \CONTEXTS ::= (\domMap \in \COMPONENTS \rightarrow \STKDOMS) \times (\rts \in \listT (\mathit{TL} \times \target)) \]

We add a rule to handle {\sc SetJump} annotations, and modify the {\sc Call} rule to insert {\sc CR} labels into the
return stack.
\judgment[]
         {\(\codemap ~ (\mach ~ \PCname) = {\sc SetJump}\)}
         {\(\mach,(\domMap,\rts) \stepsto_C \domMap',(\text{\sc EX}, \retcon ~ \mach)::\rts\)}
\judgmenttwobrlong[]
              {\(\codemap ~ (\mach ~ \PCname) = \callmap\)}
              {\(\components = \{\component | \sealcon ~ \mach[\component]\}\)}
              {\(\domMap' = \domMap[\components \mapsto \sealed{|\rts|}]\)}
              {\(\mach,(\domMap,\rts) \stepsto_C \domMap',(\text{\sc CR}, \retcon ~ \mach)::\rts\)}
The return rules operate identically regardless of the target labels.

\definition
We define \textbf{\em stepwise stack integrity}, \textbf{\em stepwise stack confidentiality},
\textbf{\em observational stack integrity}, \textbf{\em observational stack confidentiality},
in the same way as in the core model, substituting the above \(\CONTEXTS\) type and update
function for their original.

\definition
A system enjoys \textit{\textbf{well-bracketed control flow}} with exceptions when, for every reachable state
\(\mpcstatename\) where \(\pi_\context(\mpcstatename) = (\underscore,\rts)\), and
\(\mpcstatename \stepsto \mpcstatename'\) where \(\pi_\context(\mpcstatename') = (\underscore,\rts')\),
if \(|\rts'| < |\rts|\), then either \(|\rts'| = |\rts|-1\) or \(\rts = \underscore +\!\!+ (\text{\sc EX},\underscore) +\!\!+ \rts'\).
